\textbf{NBA Party}

### 2017-04-13 init_model.rnw
Fixed issue concerning 'simple.date' and merging in ESPN data. Added ideas for models, which have now been moved to explore_starters.r

<<>>=
HOURS <- 24
m <- glm(outcome == 'W' ~ I(nmusicians*(nhours.lgame <= HOURS)), 
         data = lines[season < 2017 & last.game.loc != team])

@@

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = lines[season == 2017 & nhours.lgame <= HOURS & last.game.loc != team], 
             type = 'response')
p <- ifelse(p < .45, 0, 1)
table(round(p), lines[season == 2017 & nhours.lgame <= HOURS & last.game.loc != team, outcome])

@@

lines[nhours.lgame <= 36, mean(tpa), by = last.game.loc][order(V1)]
lines[nhours.lgame <= 36, mean(tps), by = last.game.loc][order(V1)]
lines[nhours.lgame <= 36, mean(tps) - mean(tpa), by = last.game.loc][order(V1)]

@@

>>>>

<<>>=
HOURS <- 36
m <- glm(outcome == 'W' ~ I(nmusicians*(nhours.lgame <= HOURS)), 
         data = lines[season < 2017 & last.game.loc != team])

@@

### We're only interested in making predictions when teams party.
p <- predict(m, newdata = lines[season == 2017 & nhours.lgame <= HOURS & last.game.loc != team], 
             type = 'response')
table(round(p), lines[season == 2017 & nhours.lgame <= HOURS & last.game.loc != team, outcome])

@@

## lines[nhours.lgame <= 36, mean(tpa), by = last.game.loc][order(V1)]
## lines[nhours.lgame <= 36, mean(tps), by = last.game.loc][order(V1)]
## lines[nhours.lgame <= 36, mean(tps) - mean(tpa), by = last.game.loc][order(V1)]

##################################################
### musicians per log population
##################################################

@@

##################################################
### ESPN
##################################################

espn <- fread('tmp_data/espn_player_data.csv')
espn[, date := as.Date(date)]
lines[, simple.date := as.character(date) %>% substr(., 1, 10) %>% as.Date]
data <- merge(lines, espn, by.x = c('team', 'simple.date'), by.y = c('team', 'date'), all.x = T) ### Careful which obs we keep!

data[, dmeaned.free  := free.made/min - mean(free.made/min), by = list(starters, season)]
data[, dmeaned.three := three.made/min - mean(three.made/min), by = list(starters, season)]
data[, dmeaned.reb   := reb / min - mean(reb / min), by = list(starters, season)]
data[, dmeaned.oreb   := oreb / min - mean(oreb / min), by = list(starters, season)]
data[, dmeaned.dreb   := dreb / min - mean(dreb / min), by = list(starters, season)]
data[, dmeaned.pts   := pts / min - mean(pts / min,na.rm=T), by = list(starters, season)]

data[, chg.pos := three.made + fg.made + free.attempted/2 + 
           to + (fg.attempted-fg.made + three.attempted - three.made - oreb)]

changes <- data[, list(ttl.chg.pos = sum(chg.pos)), 
            keyby = list(season, team, date, opponent)]
lines <- merge(lines, changes, by = c('season', 'team', 'date', 'opponent'))

setkey(lines, season, team, date)
lines[, lag.chg.pos := c(NA, lag(ttl.chg.pos)[1:.N-1]), by = list(season, team)]

glm(outcome == 'W' ~ party + nhours.lgame + I(log(travel.dist+1)) + lag.chg.pos,
    data = lines[season < 2017 & last.game.loc != team], family = 'binomial') %>% summary

setnames(data, '+/-', 'pm')

lm(dmeaned.three ~ party, data = data[season < 2017 & last.game.loc != team]) %>% summary
lm(dmeaned.reb ~ party, data = data[season < 2017 & last.game.loc != team]) %>% summary
lm(dmeaned.dreb ~ party, data = data[season < 2017 & last.game.loc != team]) %>% summary

data[, pm := as.numeric(pm)]
data[, pf := as.numeric(pf)]
### WOW! Earn 1-2 points less per minute on average. (Further condition on player position?)
### Next goal: we should be able to recover our grand mean estimate above. That is, test model efficacy 
### by predicting the number of points a team will score using ex-ante minutes of play-time.
lm(I(pm / min) ~ party, data = data[season < 2017 & last.game.loc != team]) %>% summary

lm(dmeaned.pts ~ party, data = data[season < 2017 & last.game.loc != team]%>%na.omit) %>% summary

## data[grep("(los angeles)|(new york)|(brooklyn)", last.game.loc), 
##      list(average.dmeaned.dreb = mean(dmeaned.dreb)), by = starters][order(average.dmeaned.dreb)] %>%
##     write.csv(., file = 'dmeaned.dreb.csv')

## data[grep("(los angeles)|(new york)|(brooklyn)", last.game.loc), 
##      list(average.dmeaned.pts = mean(dmeaned.pts)), by = starters][order(average.dmeaned.pts)] %>%
##     write.csv(., file = 'dmeaned.pts.csv')
